```{r}
#| label: setup
#| include: false

library(here)

here("R", ".setup.R") |> source()
```

## Overview

This document describes the processes for managing [PMTiles](https://docs.protomaps.com/pmtiles/) files created in this project, including integrity testing, listing files, and uploading or deleting files from the R2 bucket.

## Methods

### Code Style

The Tidyverse [tidy tools manifesto](https://tidyverse.tidyverse.org/articles/manifesto.html) [@wickham2023c], [code style guide](https://style.tidyverse.org/) [@wickhama] and [design principles](https://design.tidyverse.org/) [@wickhamc] were followed to ensure consistency and enhance readability.

### Reproducibility

The pipeline is fully reproducible and can be run again at any time. To ensure consistent results, the [`renv`](https://rstudio.github.io/renv/) package [@ushey2025] is used to manage and restore the R environment. See the [README](https://github.com/cem-usp/pmtilesbr/blob/main/README.md) file in the code repository to learn how to run it.

## Set Environment

### Load Packages

```{r}
#| label: Set Environment
#| output: false

library(cli)
library(fs)
library(here)
library(magrittr)
library(pmtiles) # github.com/walkerke/pmtiles
library(purrr)
library(stringr)
library(yaml)
```

### Load Custom Functions

```{r}
here("R", "r2_delete_folder.R") |> source()
here("R", "r2_delete_object.R") |> source()
here("R", "r2_list_bucket.R") |> source()
here("R", "r2_list_objects.R") |> source()
here("R", "r2_upload_file.R") |> source()
```

### Set Data Directory

```{r}
data_dir <- here("pmtiles")
```

### Set Parameters

```{r}
yaml_file <- here("pmtiles.yaml")
```

```{r}
collection <- NULL
```

```{r}
year <- NULL
```

```{r}
simplified <- NULL
```

## Update `pmtiles.yaml`

```{r}
#| label: Update `pmtiles.yaml`

yaml_file |> r2_list_bucket()
```

## Test and Delete Corrupted Files

### List Files

```{r}
#| label: Test and Delete Corrupted Files

files <-
  data_dir |>
  dir_ls(
    type = "file",
    recurse = TRUE,
    glob = "*.pmtiles"
  )
```

```{r}
if (!is.null(collection)) {
  files <-
    data_dir |>
    file.path(collection) |>
    dir_ls(
      type = "file",
      recurse = TRUE,
      glob = "*.pmtiles"
    )
}
```

```{r}
if (!is.null(year)) {
  files <-
    files |>
    str_subset(
      paste0("year-", year)
    )
}
```

```{r}
if (!is.null(simplified)) {
  files <-
    files |>
    str_subset(
      paste0("simplified-", simplified)
    )
}
```

### Test Files

```{r}
#| eval: false

cli_progress_bar(
  name = "Testing PMTiles",
  total = length(files)
)

corrupted_files <- character()

for (i in files) {
  test <-
    i |>
    pm_show(tilejson = TRUE) |>
    try(silent = TRUE)

  if (inherits(test, "try-error")) {
    corrupted_files <- c(corrupted_files, i)
  }

  cli_progress_update()
}

cli_progress_done()
```

```{r}
corrupted_files |> length()
```

### Delete Files

```{r}
#| eval: false

corrupted_files |> file_delete()
```

## List Files

```{r}
#| label: List Files

yaml_data <- read_yaml(yaml_file)
```

```{r}
local_files <-
  data_dir |>
  dir_ls(
    type = "file",
    recurse = TRUE,
    glob = "*.pmtiles"
  ) |>
  path_rel(data_dir) |>
  as.character()
```

```{r}
hosted_files <-
  yaml_data |>
  pluck("objects") |>
  map(\(x) x |> pluck("key")) |>
  unlist() |>
  str_subset("\\.pmtiles$")
```

```{r}
local_files |> equals(hosted_files) |> all()
```

```{r}
# Missing files
local_files |> setdiff(hosted_files) |> length()
```

```{r}
# Orphan files
hosted_files |> setdiff(local_files) |> length()
```

## Upload Missing Files

### List Files

```{r}
#| label: Upload Missing Files

missing_files <-
  local_files %>%
  setdiff(hosted_files) %>%
  file.path(data_dir, .)
```

```{r}
missing_files |> length()
```

```{r}
missing_files |> head()
```

### Upload Files

```{r}
#| eval: false

missing_files |>
  map(
    .f = \(file) {
      file |>
        r2_upload_file(
          object_key = file |>
            path_rel(data_dir) |>
            as.character()
        )
    },
    .progress = TRUE
  )
```

## Delete Orphan Files

### List Files

```{r}
#| label: Delete Orphan Files

orphan_files <-
  hosted_files |>
  setdiff(local_files)
```

```{r}
orphan_files |> length()
```

```{r}
orphan_files |> head()
```

### Delete Files

```{r}
#| eval: false

orphan_files |>
  map(
    .f = r2_delete_object,
    .progress = TRUE
  )
```

## References {.unnumbered}

::: {#refs}
:::
