```{r}
#| label: setup
#| include: false

library(here)

here("R", ".setup.R") |> source()
```

## Overview

This document describes the testing process used after the creation of the [PMTiles](https://docs.protomaps.com/pmtiles/) files.

## Methods

### Code Style

The Tidyverse [tidy tools manifesto](https://tidyverse.tidyverse.org/articles/manifesto.html) [@wickham2023c], [code style guide](https://style.tidyverse.org/) [@wickhama] and [design principles](https://design.tidyverse.org/) [@wickhamc] were followed to ensure consistency and enhance readability.

### Reproducibility

The pipeline is fully reproducible and can be run again at any time. To ensure consistent results, the [`renv`](https://rstudio.github.io/renv/) package [@ushey2025] is used to manage and restore the R environment. See the [README](https://github.com/cem-usp/pmtilesbr/blob/main/README.md) file in the code repository to learn how to run it.

## Set the Environment

### Load Packages

```{r}
#| label: Set the Environment
#| output: false

library(cli)
library(fs)
library(here)
library(pmtiles) # github.com/walkerke/pmtiles
library(stringr)
```

### Set Data Directories

```{r}
raw_data_dir <- here("data-raw")
data_dir <- here("pmtiles")
```

```{r}
for (i in c(data_dir, raw_data_dir)) {
  if (!dir_exists(i)) {
    dir_create(i, recurse = TRUE)
  }
}
```

### Set Initial Parameters

::: {.callout-note}
The `year` variable specifies the year of the data.
:::

```{r}
year <- 2024
```

```{r}
pmtiles_dir <- data_dir
```

## Test and Delete Corrupted PMTiles

```{r}
#| label: Test and Delete Corrupted PMTiles

files <-
  pmtiles_dir |>
  dir_ls(
    type = "file",
    recurse = TRUE,
    glob = "*.pmtiles"
  ) |>
  str_subset(
    paste0("year-", year)
  )
```

```{r}
cli_progress_bar(
  name = "Testing PMTiles",
  total = length(files)
)

for (i in files) {
  test <-
    i |>
    pm_show(tilejson = TRUE) |>
    try(silent = TRUE)

  if (inherits(test, "try-error")) {
    file_delete(i)
  }

  cli_progress_update()
}

cli_progress_done()
```

## References {.unnumbered}

::: {#refs}
:::
